# Samantha Lynn Bell 2020
____________________________________________________________________________________
What does this script need?
  ____________________________________________________________________________________

This script takes in:
  1- This script takes in a ____ file from _____ that is provided by ____


____________________________________________________________________________________
What does this script do?
  ____________________________________________________________________________________
It will load the data, ____ and export:
1- [file 1]
2- [file 2] ...
__________________________________________________________________________________
INSTRUCTIONS
____________________________________________________________________________________
1- Fill in required necessary information in fields that look like this: 
  # ************************************************************************************#
  #      Text Here
  #
  # ************************************************************************************#
  2- Then click the green run button for that block of code


Provide the data and save locations
```{r}
# String in quotes, giving the path to the original raw data and the location you would like to save to later
# No file names, just path to the folder
inputLocation <- "S:/Health/Epidemiology/Data/MDSS/...."
saveLocation <- "C:/Users/Rappa/Documents"
```


```{r}
# Your code here
```

Save the export files

What is happening here?
  -the paste0() function pastes strings, with zero space between them
  -we are telling the write.xlsx function that we:
    -want to write an excel file
    -we want to print the RawAge data to this file
    -we want the file path to start with our provided location
    -we want the file path to end with the filename "myfile.xlsx" 
        The extension of the file must be given (.xslx)
```{r export}
write.xlsx(RawAge, file=paste0(location, "/myfile.xlsx")) 
```

