Load Packages
```{r}
library(tidyverse)
```


Look for addresses that pop up repeatedly. 

1- Make a simplified address for matching
    If an address has a one letter N,S,E,W capture : take the number, one letter, and a full word following (ex: 100 E Mack)
    If an address has only a number and then the name : take the number and first full word (ex: 100 Mack)
2- Group the simplified addresses, ignoring case

Example addresses in a table
```{r}
Id <- c(1:16)
Street_Address <- c("444 Michigan Avenue","11570 East Warren Ave","4000 South Jean Street","411 W Lafayette","8060 W Vernor","8060 West Vernor","11570 E Warren Avenue","135000 W. Chicago","135000 West Chicago Ave","19333 W 8 Mile","19333 West 8 Mile","13233 East Jefferson Ave","13233 E Jefferson","13233 Jefferson Avenue","13335 W. Warren","13335 West Warren Ave")
myData <- as_tibble(cbind(Id, Street_Address))
```


Clean the addresses and group them
```{r}
# Make a column with just the beginning of street addresses (for easier grouping)
pat1 <- "^\\d+\\s+[N|S|E|W].{0,5}\\s*\\w+"  #match for a one letter N,S,E,W before the name
pat2 <- "^\\d+\\s+\\w+" #match for full word directly after the number - only use if not expecting a directional letter

myData$Address_Simple <- ""  # initiate empty column

for(i in 1:dim(myData)[1]){
  if(!is.na(myData$Street_Address[i])){
    myData$Address_Simple[i] <- ifelse(
      !is.na(str_match(myData$Street_Address[i], regex(pat1, ignore_case = TRUE))[1]), #Check for N,S,E,W type letter match
      (str_match(myData$Street_Address[i], regex(pat1, ignore_case = TRUE))[1] %>% #if N,S,E,W letter was found, match pattern 1 and substitute NSEW to standard format
        gsub("N\\s|N\\.\\s|North\\s", "North ", x = ., ignore.case = TRUE) %>%
        gsub("S\\s|S\\.\\s|South\\s", "South ", x = ., ignore.case = TRUE) %>%
        gsub("E\\s|E\\.\\s|East\\s", "East ", x = ., ignore.case = TRUE) %>%
        gsub("W\\s|W\\.\\s|West\\s", "West ", x = ., ignore.case = TRUE)), 
      str_match(myData$Street_Address[i], regex(pat2, ignore_case = TRUE))) #else take a full word after the number using pattern 2
    }else{"NA"} # If no address, NA simple address
}
  
# Count repeat employer street addresses (make all lowercase for grouping - using tolower )
hotspots <- myData  %>%  group_by(tolower(Address_Simple)) %>% summarise(n = n()) %>% arrange(desc(n))
```


